Guide for manual trajectory inference

### 2018-06-27 scripts/evaluate_toy/1-methods-toys.Rmd
reorganise dynalysis

```{r}
# results <- PRISM::qsub_lapply(names(method_ti_methods), function(method_name) {
results <- purrr::map(method_names, function(method_name) {
  library(dyneval)

@@

  # factory(function() {
    dyneval:::evaluate_ti_method(tasks, method, params, metrics = metric_names, timeout = 100)
  # }
  # )()
})
# }, qsub_environment = list2env(lst(method_ti_methods, tasks, metric_names, method_params)), qsub_config = PRISM::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```

>>>>

```{r}
# results <- qsub::qsub_lapply(names(method_ti_methods), function(method_name) {
results <- purrr::map(method_names, function(method_name) {
  library(dyneval)

@@

  # factory(function() {
    dyneval:::evaluate_ti_method(tasks, method, params, metrics = metric_names, timeout = 100)
  # }
  # )()
})
# }, qsub_environment = list2env(lst(method_ti_methods, tasks, metric_names, method_params)), qsub_config = qsub::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```

### 2018-06-27 scripts/evaluate_toy/2-methods-plots.Rmd
reorganise dynalysis

```{r}
plot_method <- function(model, method_name) {
  print(method_name)
  plot_fun <- method_descriptions[[method_name]]$plot_fun

@@

method_descriptions <- map(scores$method_id, ~get(paste0("description_", .))()) %>% set_names(scores$method_id)
plots <- map2(scores$model, scores$method_id, plot_method)
```

>>>>

```{r}
plot_method <- function(model, method_name) {
  print(method_name)
  plot_fun <- method_ti_methods[[method_name]]$plot_fun

@@

method_ti_methods <- map(scores$method_id, ~get(paste0("ti_", .))()) %>% set_names(scores$method_id)
plots <- map2(scores$model, scores$method_id, plot_method)
```

### 2018-06-27 scripts/manual_ti/guide.Rmd
reorganise dynalysis

When we assume that cells go through this process gradually, the expression changes will follow a continuum, and this will be reflected in the 2D visualisation of the cells. Cells will follow paths within this 2D visualisation, but due to heterogeneity, will not exactly follow the path. See for example the red path in the following visualisation;

@@

You don't have to define an end or start point. When drawing cycles, splits or convergences, two points don't have to lie at exactly the same position, as they will be mergen computationally.

@@

>>>>

When we assume that cells go through this process gradually, the expression changes will follow a continuum, and this will be reflected in the 2D visualisation of the cells. Cells will follow paths within this 2D visualisation, but due to heterogeneity, will not exactly lie on this "average" path. See for example the red path in the following visualisation:

@@

You don't have to define an end or start point. When drawing cycles, splits or convergences, two points don't have to lie at exactly the same position, as they will be merged computationally.

@@

Thank you!
